Examining background gene list issue in clusterProfiler - RNA-seq example

### 2024-07-09 analysis/analyse_rnaseq1.Rmd
pdf1

@@

>>>>

pdf("fig1_ORAsig.pdf",width=7,height=7)
par(mar=c(c(5.1, 7.1, 2.1, 2.1) ))
barplot(t(df),beside=TRUE,horiz=TRUE,las=1,xlim=c(0,1250),
  xlab="no. significant sets",
  col=c("gray30","gray80"))
text(df$ns1+50,((1:nrow(df))*3)-1.5,labels=signif(df[,1],3))
text(df$ns2+50,((1:nrow(df))*3)-0.5,labels=signif(df[,2],3))
#abline(v=seq(100,1000,100),lty=2,lwd=0.5,col="gray")
legend("bottomright", inset=.02, legend=c("corrected","original"),
  fill=c("gray80","gray30"), horiz=FALSE, cex=1.1)

@@

pdf("fig1_ORAjac.pdf",width=7, height=7)
par(mar=c(c(5.1, 5.1, 2.1, 2.1) ))
plot(cov,jac2,xlim=c(0,30000),ylim=c(0,1),pch=19,col="lightgray",cex=3,
  xlab="gene coverage",ylab="Jaccard index")
text(cov,jac2,labels=names(cov))
mylm <- lm(jac2~cov)
abline(mylm,lty=2,lwd=2)
SLOPE=unname(signif(mylm$coefficients[2],3))
INT=unname(signif(mylm$coefficients[1],3))
PVAL=signif(summary(mylm)$coefficients[4],3)
RSQ=signif(summary(mylm)$r.squared,3)
HEADER=paste("Rsq =",RSQ,"; p-val =",PVAL)
mtext(HEADER)
dev.off()
```
